---
title: "Binary logistic regression"
date: " Last edited: `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cosmo
    toc: true
    number_sections: true
    code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = " ", collapse = FALSE,
                      message=FALSE, warning=FALSE)

# Libraries
library(tidyverse)
library(janitor)
library(wooldridge)
library(gujarati)

```


# Ojective of logistic regression

Logistic regression is a multiple regression but with an outcome variable that is categorical variable and predictor variables that are continuos or categorical. It a technique with the purpose of classifying objects into distinct groups based on the characteristics. The ultimate goal of prediction is not a specific metric value, like in multiple regression, but instead a method of placing each observation into a distinct category or group.


The standard logistic regression function for predicting the outcome of an observatino given a predictor is an s-shaped curve defined as:

$$ p  = \frac{\exp(y)}{1 + \exp(y)}$$

wherein:

- $y = b_0 + b_1x$
- $\exp()$ is the exponential
- $p$ is the probability of event to occur (1) given $x$

```{r}
crime <- 
crime1 %>% filter(narr86 < 2) %>% tibble()

glm(narr86 ~ pcnv + avgsen + tottime + ptime86 + qemp86, 
    data = crime, family = binomial(link = "logit")) %>% 
     summary()

lm(narr86 ~ pcnv + avgsen + tottime + ptime86 + qemp86, 
    data = crime) %>% 
     summary()
```




# Assumptions of logistic regression



# Estimation and assessing overall fit

### Loading the required packages {-}

```

library(tidyverse)
library(wooldridge)

```

### Simple logistic regression {-}

```{r}
grade_data <- gujarati::Table15_7 %>% 
     clean_names() %>% 
     tibble() %>% 
     mutate(across(obs:grade, ~as.character(.x))) %>% 
     mutate(across(obs:grade, ~as.numeric(.x)))
     

model <- glm(grade ~ tuce, data = grade_data, family = binomial(link = "logit"))
summary(model)
```


```{r}
equatiomatic::extract_eq(model)
```


# Interpretation of results



